\documentclass{article}
    \input{../Directory_Tex_Files/AuxilliaryStuff.tex}
    \setupdirectory
    %\usepackage[margins=10pt]{geometry}
    \newgeometry{margin=0.75in}
    \input{../Directory_Tex_files/BinderCover.tex}
    \begin{document}\companybindercover{3M}
    \companybindercover{4flow, inc.}
    \companybindercover{Accenture}
    \companybindercover{Air Liquide}
    \companybindercover{Akuna Capital}
    \companybindercover{Amazon}
    \companybindercover{American Express}
    \companybindercover{Andreesen Horowitz}
    \companybindercover{Applied Predictive Technologies}
    \companybindercover{Aristeo Construction Company}
    \companybindercover{ARM, Inc.}
    \companybindercover{Arup}
    \companybindercover{Atwell}
    \companybindercover{Auto-Owners Insurance Company}
    \companybindercover{Avencore}
    \companybindercover{Axalta Coating Systems}
    \companybindercover{Barnett Capital / SBB Research Group}
    \companybindercover{BASF Corporation}
    \companybindercover{Black \& Veatch}
    \companybindercover{Bloomberg LP}
    \companybindercover{Bosch}
    \companybindercover{BP Americas}
    \companybindercover{BP3 Global, Inc}
    \companybindercover{Brady Corporation}
    \companybindercover{Capital One}
    \companybindercover{Caterpillar, Inc.}
    \companybindercover{Charles River Development}
    \companybindercover{CHP Consulting Inc}
    \companybindercover{Cisco Systems}
    \companybindercover{Citadel Investment Group}
    \companybindercover{Citrix}
    \companybindercover{CME Group}
    \companybindercover{Continental Automotive}
    \companybindercover{Cummins Inc.}
    \companybindercover{Cymer, an ASML company}
    \companybindercover{Daimler/ Detroit Diesel}
    \companybindercover{Danaher Corporation}
    \companybindercover{Dell}
    \companybindercover{Delta Dental of Michigan}
    \companybindercover{Denso International America}
    \companybindercover{Discover Financial Services}
    \companybindercover{DISH Network}
    \companybindercover{Dow Chemical USA}
    \companybindercover{DRW Trading Group}
    \companybindercover{Dwyer Instruments}
    \companybindercover{Eaton Corporation}
    \companybindercover{Eli Lilly and Company}
    \companybindercover{Enova}
    \companybindercover{Ernst \& Young}
    \companybindercover{Evonik Corporation}
    \companybindercover{Exponent}
    \companybindercover{Facebook}
    \companybindercover{FactSet Research Systems Inc.}
    \companybindercover{FANUC America Corporation}
    \companybindercover{Fast Enterprises, LLC}
    \companybindercover{Fitbit}
    \companybindercover{FM Global}
    \companybindercover{Ford Motor Company}
    \companybindercover{G.W Lisk, Inc}
    \companybindercover{Garmin International}
    \companybindercover{General Dynamics, Bath Iron Works}
    \companybindercover{GENERAL ELECTRIC - GE}
    \companybindercover{General Mills}
    \companybindercover{General Motors}
    \companybindercover{Google}
    \companybindercover{Grainger}
    \companybindercover{Groupon}
    \companybindercover{Hacker Fellows}
    \companybindercover{HARMAN}
    \companybindercover{HDR Inc.}
    \companybindercover{Honda R\&D Americas, Inc.}
    \companybindercover{Honeywell}
    \companybindercover{Indeed}
    \companybindercover{Intel Corporation}
    \companybindercover{Intentional Software Corporation}
    \companybindercover{Johns Hopkins Applied Physics Laboratory (APL)}
    \companybindercover{Johnson \& Johnson}
    \companybindercover{JP Morgan Chase}
    \companybindercover{Kellogg Company}
    \companybindercover{Key Safety Systems}
    \companybindercover{Lear Corporation}
    \companybindercover{Leidos}
    \companybindercover{Levant Power Corporation}
    \companybindercover{LG Electronics}
    \companybindercover{LiveRamp}
    \companybindercover{LLamasoft, Inc.}
    \companybindercover{LMI}
    \companybindercover{\url{Lob.com}}
    \companybindercover{Lutron Electronics Co. Inc.}
    \companybindercover{MAHLE Industries, Inc.}
    \companybindercover{Manhattan Associates, Inc.}
    \companybindercover{Mathworks}
    \companybindercover{McDonnell Boehnen Hulbert \& Berghoff LLP}
    \companybindercover{MDA Information Systems LLC}
    \companybindercover{Meraki}
    \companybindercover{Microsoft}
    \companybindercover{Moeller Aerospace}
    \companybindercover{National Security Agency}
    \companybindercover{{\fontsize{30}{36}\selectfont Naval Nuclear Laboratory (Operated by Bechtel Marine Propulsion Corporation)}}
    \companybindercover{Naval Sea Systems Command (NAVSEA)}
    \companybindercover{Nexteer Automotive}
    \companybindercover{NextEra Energy, Inc.}
    \companybindercover{Nike}
    \companybindercover{Nutanix}
    \companybindercover{Oak Ridge National Laboratory}
    \companybindercover{One North Interactive}
    \companybindercover{Optiver US LLC}
    \companybindercover{Palo Alto Networks}
    \companybindercover{Perrigo}
    \companybindercover{PolyOne Corporation}
    \companybindercover{Pratt And Whitney}
    \companybindercover{Pure Storage}
    \companybindercover{PwC}
    \companybindercover{QGenda, Inc.}
    \companybindercover{QuadMetrics, Inc.}
    \companybindercover{Qualtrics}
    \companybindercover{Red Flint Group, LLC}
    \companybindercover{Redfin}
    \companybindercover{Reply Inc.}
    \companybindercover{RetailMeNot, Inc.}
    \companybindercover{Reverie}
    \companybindercover{Robinhood}
    \companybindercover{Rockwell Automation}
    \companybindercover{Ropes \& Gray}
    \companybindercover{Sandia National Labs}
    \companybindercover{SC Johnson}
    \companybindercover{Sears Holdings Corporation}
    \companybindercover{Shell}
    \companybindercover{Spot Trading L.L.C.}
    \companybindercover{Stonefield Engineering \& Design}
    \companybindercover{Stryker}
    \companybindercover{Sumitomo Electric Wiring Systems, Inc.}
    \companybindercover{Target}
    \companybindercover{Tata Consultancy Services}
    \companybindercover{TD Ameritrade}
    \companybindercover{Technology Services Group}
    \companybindercover{TechSmith Corporation}
    \companybindercover{Texas Instruments}
    \companybindercover{Textron}
    \companybindercover{The Keystone Group}
    \companybindercover{The Kraft Heinz Company}
    \companybindercover{The Lee Company}
    \companybindercover{Twilio}
    \companybindercover{Tyler Technologies}
    \companybindercover{Unilever}
    \companybindercover{Union Pacific Railroad}
    \companybindercover{United Airlines}
    \companybindercover{Uptake Technologies, Inc}
    \companybindercover{US Army Medical Department- Ann Arbor}
    \companybindercover{Vector CANtech}
    \companybindercover{VMware}
    \companybindercover{Wayfair}
    \companybindercover{Whirlpool Corporation}
    \companybindercover{Wolverine Trading, LLC}
    \companybindercover{Woodward}
    \companybindercover{X By 2}
    \companybindercover{Yanfeng Global Automotive Interiors}
    \companybindercover{Yelp, Inc.}
    \companybindercover{ZF North America, Inc.}
    \companybindercover{ZS Associates}
    \companybindercover{Western Digital}
    \companybindercover{3Red}
    \companybindercover{ABS - American Bureau of Shipping}
    \companybindercover{Administrative Controls Management, Inc.}
    \companybindercover{ADP (Automatic Data Processing)}
    \companybindercover{Advantage Computing Systems, Inc.}
    \companybindercover{Air Products and Chemicals, Inc.}
    \companybindercover{Aisin World Corp of America}
    \companybindercover{AK Steel}
    \companybindercover{Alcoa}
    \companybindercover{Allegion}
    \companybindercover{Altair Engineering Inc.}
    \companybindercover{AMD}
    \companybindercover{American Bridge Company}
    \companybindercover{Analog Devices}
    \companybindercover{Anheuser Busch InBev}
    \companybindercover{ANSYS}
    \companybindercover{AppFolio Inc.}
    \companybindercover{Applied Materials}
    \companybindercover{Arbor Networks}
    \companybindercover{AT\&T}
    \companybindercover{AUSTALUSA, LLC}
    \companybindercover{AutoForm Engineering USA, Inc.}
    \companybindercover{BAE Systems}
    \companybindercover{Ball Aerospace}
    \companybindercover{Barr Engineering Co.}
    \companybindercover{Bauer Controls}
    \companybindercover{Baxter Healthcare Corporation}
    \companybindercover{BD (Becton, Dickinson \& Company)}
    \companybindercover{Belvedere Trading}
    \companybindercover{BlackRock}
    \companybindercover{BMW Technology Corporation}
    \companybindercover{Boeing}
    \companybindercover{BorgWarner}
    \companybindercover{Bose Corporation}
    \companybindercover{Bostik, Inc.}
    \companybindercover{Breakthru Beverage Group}
    \companybindercover{Brose}
    \companybindercover{Cardinal Health}
    \companybindercover{CareEvolution}
    \companybindercover{Cavium}
    \companybindercover{Chevron Corporation}
    \companybindercover{Chicago Trading Company}
    \companybindercover{Civis Analytics}
    \companybindercover{CNA}
    \companybindercover{Cognizant Technology Solutions}
    \companybindercover{Comerica Bank}
    \companybindercover{Consumers Energy}
    \companybindercover{Control-Tec}
    \companybindercover{Cor Medical Ventures}
    \companybindercover{Coursera}
    \companybindercover{Coveris}
    \companybindercover{CSX}
    \companybindercover{Daily Thermetrics}
    \companybindercover{DaVita}
    \companybindercover{Deloitte}
    \companybindercover{Delphi}
    \companybindercover{Delta Air Lines}
    \companybindercover{Deutsche Bank}
    \companybindercover{Disher}
    \companybindercover{Domino's Pizza}
    \companybindercover{DTE Energy}
    \companybindercover{Dynacast International}
    \companybindercover{ECHELON CONSULTING}
    \companybindercover{Eldon Water}
    \companybindercover{Environmental Systems Design, Inc.}
    \companybindercover{Epic}
    \companybindercover{ExtraHop Networks}
    \companybindercover{ExxonMobil Corporation}
    \companybindercover{FAAC Incorporated}
    \companybindercover{FEV, Inc.}
    \companybindercover{Fiat Chrysler Automobiles}
    \companybindercover{Fidessa Corporation}
    \companybindercover{Fincantieri Marine Group}
    \companybindercover{Flex}
    \companybindercover{Flex N Gate}
    \companybindercover{Geely Auto}
    \companybindercover{Gibbs \& Cox}
    \companybindercover{GKN Driveline NA Inc.}
    \companybindercover{Global Prior Art, Inc.}
    \companybindercover{Goldman Sachs}
    \companybindercover{Harris Corporation}
    \companybindercover{Hemlock Semiconductor}
    \companybindercover{Herman Miller, Inc}
    \companybindercover{Hitachi Automotive Systems Americas, Inc.}
    \companybindercover{Hormel Foods Corporation}
    \companybindercover{Hughes Network Systems, LLC}
    \companybindercover{Huntington Ingalls Industries}
    \companybindercover{IBM}
    \companybindercover{Idaho National Laboratory}
    \companybindercover{Intrepid Control Systems, Inc.}
    \companybindercover{Isuzu}
    \companybindercover{IXL Learning}
    \companybindercover{Jackson National Life Insurance}
    \companybindercover{Jet Propulsion Laboratory}
    \companybindercover{Johnson Control}
    \companybindercover{Karem Aircraft, Inc.}
    \companybindercover{L-3 Mustang Technology}
    \companybindercover{Learning A-Z}
    \companybindercover{Lockheed Martin}
    \companybindercover{Manhard Consulting}
    \companybindercover{MC3 Cardiopulmonary}
    \companybindercover{Meritor, Inc.}
    \companybindercover{Michelin North America}
    \companybindercover{Michigan Department of Transportation}
    \companybindercover{MIT Lincoln Laboratory}
    \companybindercover{Mitsubishi Electric Automotive America}
    \companybindercover{Moog, Inc.}
    \companybindercover{Morningstar, Inc.}
    \companybindercover{Motorola Solutions}
    \companybindercover{Mu Sigma Inc}
    \companybindercover{National Instruments}
    \companybindercover{Naval Research Laboratory}
    \companybindercover{Navistar}
    \companybindercover{Navy Recruiting District}
    \companybindercover{NetSuite}
    \companybindercover{Newell Rubbermaid}
    \companybindercover{Nielsen}
    \companybindercover{Nissan}
    \companybindercover{NORMA Group AG}
    \companybindercover{North American Lighting}
    \companybindercover{Novacoast}
    \companybindercover{NOVI Energy}
    \companybindercover{NSK Corporation}
    \companybindercover{NVIDIA}
    \companybindercover{Old Mission Capital LLC}
    \companybindercover{Orbital ATK}
    \companybindercover{Owens Corning}
    \companybindercover{PACCAR}
    \companybindercover{Pittsburgh Glass Works (PGW)}
    \companybindercover{PJM Interconnection}
    \companybindercover{Plastic Omnium}
    \companybindercover{POWER Engineers, Inc.}
    \companybindercover{Pratt \& Miller}
    \companybindercover{Procter \& Gamble}
    \companybindercover{Qumulo}
    \companybindercover{Raytheon}
    \companybindercover{Riot Games}
    \companybindercover{Rolls-Royce}
    \companybindercover{Sachse Construction}
    \companybindercover{SAFE Boats International}
    \companybindercover{Salesforce}
    \companybindercover{Schlumberger}
    \companybindercover{Siemens PLM Software}
    \companybindercover{Silicon Labs}
    \companybindercover{Skyworks Solutions, Inc.}
    \companybindercover{Snowflake Computing}
    \companybindercover{SpaceX}
    \companybindercover{Sparrow Health System IT Department}
    \companybindercover{SpotHero}
    \companybindercover{SSC PACIFIC}
    \companybindercover{St. Jude Medical}
    \companybindercover{Structural Group}
    \companybindercover{The Aerospace Corporation}
    \companybindercover{The Dennis Group}
    \companybindercover{The Kresge Foundation}
    \companybindercover{The MITRE Corporation}
    \companybindercover{Thomson Reuters}
    \companybindercover{Toyota}
    \companybindercover{TransMarket Group LLC}
    \companybindercover{U.S. Army Healthcare}
    \companybindercover{U.S. Patent and Trademark Office}
    \companybindercover{Uniform Color Company}
    \companybindercover{United States Air Force}
    \companybindercover{US Army Aviation and Missile RDEC}
    \companybindercover{US Environmental Protection Agency}
    \companybindercover{UTC Aerospace Systems}
    \companybindercover{ViaSat Inc}
    \companybindercover{Vodori}
    \companybindercover{Whiting-Turner}
    \companybindercover{Williams International}
    \companybindercover{Workday}
    \companybindercover{Yahoo!}
    \end{document}