\documentclass{article}
    \input{../Directory_Tex_Files/AuxilliaryStuff.tex}
    \setupdirectory
    %\usepackage[margins=10pt]{geometry}
    \newgeometry{margin=0.75in}
    \input{../Directory_Tex_files/BinderCover.tex}
    \begin{document}\companybindercover{3M Company}
    \companybindercover{ABS - American Bureau of Shipping}
    \companybindercover{Accenture}
    \companybindercover{Advanced Micro Devices}
    \companybindercover{AIG}
    \companybindercover{Air Liquide}
    \companybindercover{Airbnb}
    \companybindercover{Aisin Technical Center of America}
    \companybindercover{Allston Trading}
    \companybindercover{Amazon}
    \companybindercover{American Express}
    \companybindercover{Analog Devices, Inc.}
    \companybindercover{Andreessen Horowitz}
    \companybindercover{Arbor Networks}
    \companybindercover{Aristeo Construction}
    \companybindercover{ARM, Inc.}
    \companybindercover{AT\&T}
    \companybindercover{ATS Automation}
    \companybindercover{Auto-Owners Insurance Company}
    \companybindercover{Avencore}
    \companybindercover{Axalta Coating Systems}
    \companybindercover{BAE Systems}
    \companybindercover{Barr Engineering Company}
    \companybindercover{Barracuda Networks, Inc.}
    \companybindercover{BASF Corporation}
    \companybindercover{Baxter Healthcare Corporation}
    \companybindercover{Black \& Veatch}
    \companybindercover{Bloomberg LP}
    \companybindercover{Bosch}
    \companybindercover{BP Americas}
    \companybindercover{Brady Corporation}
    \companybindercover{Capgemini}
    \companybindercover{Capital One}
    \companybindercover{Cardinal Health}
    \companybindercover{Caterpillar}
    \companybindercover{Central Intelligence Agency (CIA)}
    \companybindercover{Chicago Trading Company}
    \companybindercover{CHP Consulting Inc}
    \companybindercover{Citadel}
    \companybindercover{Colgate-Palmolive Company}
    \companybindercover{Consumers Energy}
    \companybindercover{Cree, Inc}
    \companybindercover{Cummins Inc.}
    \companybindercover{Cymer, an ASML company}
    \companybindercover{Deepfield Inc.}
    \companybindercover{Deloitte}
    \companybindercover{Delphi}
    \companybindercover{Denso International America}
    \companybindercover{Detroit Diesel Corp.}
    \companybindercover{Dow Chemical USA}
    \companybindercover{DRW Trading Group}
    \companybindercover{Eaton Corporation}
    \companybindercover{Eli Lilly and Company}
    \companybindercover{EMC}
    \companybindercover{Enercon Services, Inc.}
    \companybindercover{Enova}
    \companybindercover{Epic}
    \companybindercover{Ernst \& Young}
    \companybindercover{Exponent}
    \companybindercover{ExtraHop Networks}
    \companybindercover{Facebook}
    \companybindercover{FactSet Research Systems Inc.}
    \companybindercover{FANUC America Corporation}
    \companybindercover{Fast Enterprises, LLC}
    \companybindercover{Fitbit}
    \companybindercover{Ford Motor Company}
    \companybindercover{Freudenberg-NOK}
    \companybindercover{FTI Consulting}
    \companybindercover{Garmin International}
    \companybindercover{General Mills}
    \companybindercover{General Motors}
    \companybindercover{GKN Driveline NA Inc.}
    \companybindercover{Google}
    \companybindercover{Hanley, Flight \& Zimmerman LLC}
    \companybindercover{Harris Corporation}
    \companybindercover{HDR Inc.}
    \companybindercover{HookLogic}
    \companybindercover{hybris Software An SAP Company}
    \companybindercover{\url{Indeed.com}}
    \companybindercover{Intel Corporation}
    \companybindercover{Intent Media}
    \companybindercover{Intrepid Control Systems}
    \companybindercover{IXL Learning}
    \companybindercover{Johnson \& Johnson}
    \companybindercover{JP Morgan Chase}
    \companybindercover{Karem Aircraft}
    \companybindercover{Kraft Heinz}
    \companybindercover{L'Oreal USA}
    \companybindercover{MAHLE Behr Troy}
    \companybindercover{Marine Officer Selection Team}
    \companybindercover{Marvell Semiconductor, Inc.}
    \companybindercover{Mathworks}
    \companybindercover{McDonnell Boehnen Hulbert \& Berghoff LLP}
    \companybindercover{MDA Information Systems LLC}
    \companybindercover{Meraki Inc.}
    \companybindercover{Meritor, Inc.}
    \companybindercover{Microsoft}
    \companybindercover{Mitsubishi Electric Automotive America}
    \companybindercover{Mobis North America}
    \companybindercover{Moeller Manufacturing Company, Incorporated}
    \companybindercover{Morningstar, Inc.}
    \companybindercover{Mubea}
    \companybindercover{National Air and Space Intelligence Center}
    \companybindercover{National Instruments}
    \companybindercover{NAVSEA}
    \companybindercover{Navy Recruiting District, Michigan}
    \companybindercover{NetSuite}
    \companybindercover{New World Systems}
    \companybindercover{Nexteer Automotive}
    \companybindercover{Niowave, Inc.}
    \companybindercover{Nutanix}
    \companybindercover{Optiver US LLC}
    \companybindercover{Orbital ATK}
    \companybindercover{Palantir Technologies, Inc.}
    \companybindercover{Palo Alto Networks}
    \companybindercover{Parker Hannifin}
    \companybindercover{PepsiCo}
    \companybindercover{Perrigo}
    \companybindercover{Plastic Omnium}
    \companybindercover{Plex Systems, Inc.}
    \companybindercover{PolyOne Corporation}
    \companybindercover{PPG Industries}
    \companybindercover{Procter \& Gamble}
    \companybindercover{Pure Storage}
    \companybindercover{PwC}
    \companybindercover{QGenda, Inc.}
    \companybindercover{Reckitt Benckiser}
    \companybindercover{Redfin}
    \companybindercover{Revenue Solutions, Inc.}
    \companybindercover{Rolls-Royce}
    \companybindercover{Ropes \& Gray}
    \companybindercover{Samtec, Inc.}
    \companybindercover{SanDisk Corporation}
    \companybindercover{Schlumberger}
    \companybindercover{Shell}
    \companybindercover{Skyworks Solutions, Inc.}
    \companybindercover{Southwest Research Institute}
    \companybindercover{Spot Trading L.L.C.}
    \companybindercover{SPX Corporation}
    \companybindercover{St. Jude Medical}
    \companybindercover{Structural Group}
    \companybindercover{Stryker}
    \companybindercover{Syska Hennessy Group}
    \companybindercover{TAC Manufacturing, Inc. (TRAM Group)}
    \companybindercover{Target}
    \companybindercover{Techedge Group}
    \companybindercover{Technology Services Group}
    \companybindercover{Texas Instruments}
    \companybindercover{The Keystone Group}
    \companybindercover{The MITRE Corporation}
    \companybindercover{The Timken Company}
    \companybindercover{The Walsh Group}
    \companybindercover{{\fontsize{30}{36}\selectfont Toyota Motor Engineering \& Manufacturing North America, Inc.}}
    \companybindercover{Tripadvisor}
    \companybindercover{U.S. Nuclear Regulatory Commission}
    \companybindercover{Unilever}
    \companybindercover{Union Pacific Railroad}
    \companybindercover{United Airlines}
    \companybindercover{{\fontsize{30}{36}\selectfont US Army Aviation and Missile Research, Development and Engineering Center}}
    \companybindercover{Whirlpool Corporation}
    \companybindercover{Williams International}
    \companybindercover{Workforce Software}
    \companybindercover{X By 2, LLC}
    \companybindercover{Yahoo!}
    \companybindercover{Yelp, Inc.}
    \companybindercover{ZF TRW}
    \companybindercover{ZS Associates}
    \companybindercover{3Red}
    \companybindercover{Administrative Controls Management, Inc.}
    \companybindercover{ADP (Automatic Data Processing)}
    \companybindercover{AdvantageCS}
    \companybindercover{Air Products and Chemicals, Inc.}
    \companybindercover{Akuna Capital}
    \companybindercover{Alcoa}
    \companybindercover{Anheuser Busch InBev}
    \companybindercover{AppFolio Inc}
    \companybindercover{Apple}
    \companybindercover{Applied Materials}
    \companybindercover{Applied Predictive Technologies}
    \companybindercover{Apprenda Inc.}
    \companybindercover{Apttus}
    \companybindercover{Aruba Networks}
    \companybindercover{Arup}
    \companybindercover{athenahealth, Inc.}
    \companybindercover{Atieva}
    \companybindercover{Avery Dennison}
    \companybindercover{Bauer Controls}
    \companybindercover{BD (Becton, Dickinson \& Company)}
    \companybindercover{Bechtel}
    \companybindercover{Belvedere Trading LLC}
    \companybindercover{Bluebeam Software, Inc.}
    \companybindercover{Borg Warner}
    \companybindercover{Bose Corporation}
    \companybindercover{Bostik, Inc.}
    \companybindercover{BP3 Global, Inc}
    \companybindercover{bswift}
    \companybindercover{Calsonic Kansei}
    \companybindercover{CareEvolution}
    \companybindercover{Cavium Networks}
    \companybindercover{Charles River Development}
    \companybindercover{Chevron}
    \companybindercover{Cirrus Logic}
    \companybindercover{Cisco Systems}
    \companybindercover{Citrix Systems, Inc.}
    \companybindercover{Civis Analytics}
    \companybindercover{Clarkston Consulting}
    \companybindercover{Cleveland Clinic}
    \companybindercover{CME Group}
    \companybindercover{CNA}
    \companybindercover{Cognizant Technology Solutions}
    \companybindercover{Comau LLC}
    \companybindercover{Comerica Bank}
    \companybindercover{Continental Automotive}
    \companybindercover{Cor Medical Ventures}
    \companybindercover{Danlaw, Inc.,}
    \companybindercover{DCS Corporation}
    \companybindercover{Dell}
    \companybindercover{Deublin Company}
    \companybindercover{Deutsche Bank}
    \companybindercover{Discover Financial Services}
    \companybindercover{DISH Network}
    \companybindercover{Domino's}
    \companybindercover{Dow Corning Corporation}
    \companybindercover{DTE Energy}
    \companybindercover{Duo Security}
    \companybindercover{Dwyer Instruments}
    \companybindercover{Dynatrace}
    \companybindercover{Eldon Water}
    \companybindercover{Elektrobit}
    \companybindercover{Ensighten Inc.}
    \companybindercover{Etherios}
    \companybindercover{Etsy}
    \companybindercover{Evonik Corporation}
    \companybindercover{Expedia, Inc.}
    \companybindercover{ExxonMobil Corporation}
    \companybindercover{FEV North America, Inc.}
    \companybindercover{Fiat Chrysler Automobiles (FCA)}
    \companybindercover{Fidessa corporation}
    \companybindercover{Fincantieri Marine Group}
    \companybindercover{Flatiron Health}
    \companybindercover{G.A. Richards}
    \companybindercover{GEICO}
    \companybindercover{General Dynamics Electric Boat}
    \companybindercover{General Electric}
    \companybindercover{GHD}
    \companybindercover{Goldman Sachs}
    \companybindercover{Groupon}
    \companybindercover{Halma}
    \companybindercover{Here}
    \companybindercover{Hewlett Packard}
    \companybindercover{Hitachi Automotive Systems Americas, Inc.}
    \companybindercover{Honda R\&D Americas, Inc.}
    \companybindercover{Honeywell}
    \companybindercover{Hormel Foods Corporation}
    \companybindercover{Hughes Network Systems, LLC}
    \companybindercover{IBM}
    \companybindercover{Idaho National Laboratory}
    \companybindercover{ikaSystems Corporation}
    \companybindercover{InDepth Engineering Solutions, LLC}
    \companybindercover{Jet Propulsion Laboratory}
    \companybindercover{John Crane}
    \companybindercover{Johns Hopkins Applied Physics Lab (APL)}
    \companybindercover{Johnson Controls}
    \companybindercover{KCG Holdings, Inc.}
    \companybindercover{Lake Region Medical}
    \companybindercover{Lear Corporation}
    \companybindercover{Learning A-Z}
    \companybindercover{Leidos}
    \companybindercover{Levant Power Corporation}
    \companybindercover{LG Electronics}
    \companybindercover{LiveRamp}
    \companybindercover{LLamasoft}
    \companybindercover{LOCKHEED MARTIN}
    \companybindercover{Lutron Electronics Co., Inc.}
    \companybindercover{MailChimp}
    \companybindercover{Mainstream Engineering}
    \companybindercover{Manhattan Associates}
    \companybindercover{Meed Inc.}
    \companybindercover{Methanex}
    \companybindercover{Michelin}
    \companybindercover{Michigan Tech University}
    \companybindercover{MIT Lincoln Laboratory}
    \companybindercover{Molex}
    \companybindercover{Motorola Solutions Inc.}
    \companybindercover{Mu Sigma Inc}
    \companybindercover{National Security Agency}
    \companybindercover{Naval Nuclear Lab}
    \companybindercover{Naval Research Laboratory}
    \companybindercover{Nestle USA}
    \companybindercover{NextEra Energy, Inc.}
    \companybindercover{NSK}
    \companybindercover{One Energy}
    \companybindercover{Orbitz Worldwide}
    \companybindercover{Owens Corning}
    \companybindercover{PACCAR}
    \companybindercover{Pandora}
    \companybindercover{Plastipak Packaging}
    \companybindercover{Pratt \& Miller Engineering}
    \companybindercover{Pratt And Whitney}
    \companybindercover{Praxair, Inc.}
    \companybindercover{Qadium}
    \companybindercover{Qualtrics Labs}
    \companybindercover{Qumulo}
    \companybindercover{Raytheon}
    \companybindercover{RelateIQ}
    \companybindercover{RetailMeNot, Inc.}
    \companybindercover{Rockwell Automation}
    \companybindercover{Sachse Construction}
    \companybindercover{Sandia National Laboratories}
    \companybindercover{SapientNitro}
    \companybindercover{SBB Research Group}
    \companybindercover{SC Johnson}
    \companybindercover{shopkick}
    \companybindercover{Silicon Labs}
    \companybindercover{SME}
    \companybindercover{Soar Technology, Inc.}
    \companybindercover{SpaceX}
    \companybindercover{Sparrow Health System IT Department}
    \companybindercover{Systems \& Technology Research}
    \companybindercover{Tata Consultancy Services}
    \companybindercover{TD Ameritrade}
    \companybindercover{TechSmith Corporation}
    \companybindercover{Tesla Motors}
    \companybindercover{Tetra Tech}
    \companybindercover{Textron}
    \companybindercover{The Boeing Company}
    \companybindercover{The Lee Company}
    \companybindercover{Thomson Reuters}
    \companybindercover{Trident Maritime Systems}
    \companybindercover{Truven Health Analytics}
    \companybindercover{Twilio}
    \companybindercover{Uniform Color Company}
    \companybindercover{United States Postal Service}
    \companybindercover{Urban Science}
    \companybindercover{US Environmental Protection Agency}
    \companybindercover{Viasat, Inc.}
    \companybindercover{Visa, Inc.}
    \companybindercover{VMware}
    \companybindercover{W.W. Grainger}
    \companybindercover{Wayfair}
    \companybindercover{Wolverine Trading, LLC}
    \companybindercover{Worthington Industries}
    \companybindercover{\url{Yello.co}}
    \end{document}