\documentclass{article}
    \input{../Directory_Tex_Files/AuxilliaryStuff.tex}
    \setupdirectory
    %\usepackage[margins=10pt]{geometry}
    \newgeometry{margin=0.75in}
    \input{../Directory_Tex_files/BinderCover.tex}
    \begin{document}\companybindercover{3M}
    \companybindercover{3Red}
    \companybindercover{Accenture}
    \companybindercover{Adobe Systems}
    \companybindercover{ADP (Automatic Data Processing)}
    \companybindercover{Advanced Micro Devices}
    \companybindercover{AdvantageCS}
    \companybindercover{Air Liquide}
    \companybindercover{AirWatch}
    \companybindercover{Aisin Technical Center of America}
    \companybindercover{Amazon}
    \companybindercover{American Bureau of Shipping}
    \companybindercover{Analog Devices, Inc.}
    \companybindercover{Anheuser Busch InBev}
    \companybindercover{Answers}
    \companybindercover{ARCO/Murray Construction Company, Inc.}
    \companybindercover{Aristeo}
    \companybindercover{ARM, Inc.}
    \companybindercover{AT\&T}
    \companybindercover{Auto-Owners Insurance Company}
    \companybindercover{Avencore}
    \companybindercover{Avery Dennison}
    \companybindercover{Barr Engineering Co}
    \companybindercover{BASF}
    \companybindercover{Baxter Healthcare Corporation}
    \companybindercover{Black \& Veatch}
    \companybindercover{BMW Manufacturing Co., LLC}
    \companybindercover{Bosch}
    \companybindercover{Bose Corporation}
    \companybindercover{Bostik, Inc.}
    \companybindercover{Brady Corporation}
    \companybindercover{Bury}
    \companybindercover{Capgemini}
    \companybindercover{Capital One}
    \companybindercover{Caterpillar}
    \companybindercover{Cessna Aircraft Company}
    \companybindercover{Chartboost}
    \companybindercover{Chevron}
    \companybindercover{Chicago Trading Company}
    \companybindercover{Citadel Investment Group}
    \companybindercover{Citrix Systems, Inc.}
    \companybindercover{Clarity Solution Group}
    \companybindercover{Clarkston Consulting}
    \companybindercover{Comerica Bank}
    \companybindercover{Commonwealth Associates, Inc.}
    \companybindercover{Consumers Energy}
    \companybindercover{Cooper Tire \& Rubber company}
    \companybindercover{Cree, Inc}
    \companybindercover{Cummins Inc.}
    \companybindercover{Cymer, Inc.}
    \companybindercover{Dell}
    \companybindercover{Deloitte}
    \companybindercover{Delphi}
    \companybindercover{Denso International America}
    \companybindercover{DePuy}
    \companybindercover{Detroit Diesel Corp.}
    \companybindercover{Disher Design \& Development}
    \companybindercover{Dow Chemical}
    \companybindercover{DRW Trading Group}
    \companybindercover{DTE Energy}
    \companybindercover{Dwyer Instruments}
    \companybindercover{Eaton Corporation}
    \companybindercover{Elektrobit}
    \companybindercover{Eli Lilly and Company}
    \companybindercover{EMC}
    \companybindercover{End-to-End Analytics}
    \companybindercover{Energy Power Systems}
    \companybindercover{Enova}
    \companybindercover{Epic}
    \companybindercover{Etherios}
    \companybindercover{Ethicon Endo-Surgery}
    \companybindercover{Evonik Industries}
    \companybindercover{ExactTarget}
    \companybindercover{Exponent}
    \companybindercover{Facebook, Inc}
    \companybindercover{FTI Consulting}
    \companybindercover{Garmin International}
    \companybindercover{GEICO}
    \companybindercover{General Dynamics Advanced Information Systems}
    \companybindercover{General Dynamics Bath Iron Works}
    \companybindercover{General Dynamics Electric Boat}
    \companybindercover{General Electric}
    \companybindercover{General Mills}
    \companybindercover{Goldman Sachs}
    \companybindercover{Grand Circus Detroit, LLC}
    \companybindercover{Groupon}
    \companybindercover{H.B. Fuller Company}
    \companybindercover{Hanley, Flight \& Zimmerman LLC}
    \companybindercover{HookLogic}
    \companybindercover{Hormel Foods Corporation}
    \companybindercover{IBM}
    \companybindercover{InDepth Engineering Solutions, LLC}
    \companybindercover{Intel Corporation}
    \companybindercover{ITHAKA}
    \companybindercover{Jet Propulsion Laboratory}
    \companybindercover{JP Morgan Chase}
    \companybindercover{Jump Trading}
    \companybindercover{Jut, Inc.}
    \companybindercover{Leidos}
    \companybindercover{LHP}
    \companybindercover{L'Oreal USA}
    \companybindercover{Lutron Electronics Co., Inc.}
    \companybindercover{Magna Norplas Industries Inc.}
    \companybindercover{Magna Powertrain}
    \companybindercover{Marvell Semiconductor, Inc.}
    \companybindercover{Mathworks}
    \companybindercover{McDonnell Boehnen Hulbert \& Berghoff LLP}
    \companybindercover{MediaMath}
    \companybindercover{Meraki}
    \companybindercover{Meritor, Inc.}
    \companybindercover{{\fontsize{30}{36}\selectfont Michigan Economic Development Corporation/Pure Michigan}}
    \companybindercover{Microsoft}
    \companybindercover{Military Sealift Command}
    \companybindercover{Minnetronix, Inc.}
    \companybindercover{Molex, Incorporation}
    \companybindercover{Morningstar, Inc.}
    \companybindercover{Motorola Solutions}
    \companybindercover{MS2}
    \companybindercover{N.S. International}
    \companybindercover{NASA Glenn Research Center}
    \companybindercover{Navy Recruiting District, Michigan}
    \companybindercover{NetSuite}
    \companybindercover{New World Systems}
    \companybindercover{Nexteer Automotive}
    \companybindercover{Northern Trust}
    \companybindercover{Northrop Grumman Corporation}
    \companybindercover{NSK Corporation}
    \companybindercover{NVIDIA}
    \companybindercover{Optiver US LLC}
    \companybindercover{Orbitz Worldwide}
    \companybindercover{Parker Hannifin}
    \companybindercover{PepsiCo}
    \companybindercover{Perrigo}
    \companybindercover{Plex Systems, Inc.}
    \companybindercover{POWER Engineers, Inc.}
    \companybindercover{Pratt \& Whitney}
    \companybindercover{QGenda, Inc.}
    \companybindercover{Raytheon}
    \companybindercover{Readyforce}
    \companybindercover{Reckitt Benckiser}
    \companybindercover{Reply, Inc}
    \companybindercover{Riverbed Technology}
    \companybindercover{Sandia National Laboratories}
    \companybindercover{Say Media}
    \companybindercover{SBB Research Group}
    \companybindercover{Schlumberger}
    \companybindercover{Southwest Research Institute}
    \companybindercover{SPX Corporation}
    \companybindercover{Stryker}
    \companybindercover{Takata}
    \companybindercover{Tata Consultancy Services}
    \companybindercover{Technology Services Group}
    \companybindercover{Texas Instruments}
    \companybindercover{The Aerospace Corporation}
    \companybindercover{The Keystone Group}
    \companybindercover{The Timken Company}
    \companybindercover{{\fontsize{30}{36}\selectfont Toyota Motor Engineering \& Manufacturing North America, Inc. (TEMA)}}
    \companybindercover{Truven Health Analytics}
    \companybindercover{Twilio}
    \companybindercover{U.S. Patent and Trademark Office}
    \companybindercover{Unilever}
    \companybindercover{US EPA}
    \companybindercover{Verizon}
    \companybindercover{Vertafore}
    \companybindercover{ViaSat, Inc.}
    \companybindercover{Wayfair}
    \companybindercover{Weather Underground}
    \companybindercover{Workforce Software}
    \companybindercover{X By 2, Inc.}
    \companybindercover{Yahoo}
    \companybindercover{Yelp, Inc.}
    \companybindercover{ZS Associates}
    \companybindercover{SanDisk Corporation}
    \companybindercover{Accela}
    \companybindercover{Administrative Controls Management, Inc.}
    \companybindercover{Affirm, Inc.}
    \companybindercover{AIG}
    \companybindercover{Air Products and Chemicals, Inc.}
    \companybindercover{Alcoa}
    \companybindercover{Allston Trading LLC}
    \companybindercover{American Express}
    \companybindercover{Amway}
    \companybindercover{Andreessen Horowitz}
    \companybindercover{Apple}
    \companybindercover{Applied Materials}
    \companybindercover{Arbor Networks}
    \companybindercover{Arista Networks}
    \companybindercover{Atomic Object}
    \companybindercover{Autoliv ASP Inc.}
    \companybindercover{BAE Systems}
    \companybindercover{Baker Hughes}
    \companybindercover{Bank of America}
    \companybindercover{Barracuda Networks}
    \companybindercover{Battelle Memorial Institute}
    \companybindercover{Bauer Controls}
    \companybindercover{Bechtel Corporation}
    \companybindercover{Bechtel Marine Propulsion Corporation}
    \companybindercover{Belcan}
    \companybindercover{Belden}
    \companybindercover{Bloomberg LP}
    \companybindercover{Bluebeam Software, Inc.}
    \companybindercover{BorgWarner}
    \companybindercover{BP America}
    \companybindercover{Broadcom Corporation}
    \companybindercover{Brose North America, INC.}
    \companybindercover{Cardinal Health}
    \companybindercover{CareEvolution}
    \companybindercover{Caterpillar}
    \companybindercover{Cavium Networks}
    \companybindercover{Charles River Development}
    \companybindercover{CHP Consulting Inc}
    \companybindercover{Chrysler Group LLC}
    \companybindercover{Cisco Systems}
    \companybindercover{Civis Analytics}
    \companybindercover{CME Group}
    \companybindercover{Cognizant Technology Solutions}
    \companybindercover{Colgate-Palmolive}
    \companybindercover{Conestoga-Rovers \& Associates}
    \companybindercover{Continental Automotive}
    \companybindercover{Cook Nuclear Plant}
    \companybindercover{CoverMyMeds}
    \companybindercover{DCS Corp}
    \companybindercover{Delta Air Lines}
    \companybindercover{Discover Financial Services}
    \companybindercover{Domino's Pizza}
    \companybindercover{Dow Corning Corporation}
    \companybindercover{eBay, Inc.}
    \companybindercover{Echelon Consulting, LLC}
    \companybindercover{Eldon Water Inc.}
    \companybindercover{Electronic Arts}
    \companybindercover{Enercon Services, Inc}
    \companybindercover{Exa Corporation}
    \companybindercover{Expedia Inc.}
    \companybindercover{ExtraHop Networks}
    \companybindercover{ExxonMobil Corporation}
    \companybindercover{FactSet Research Systems Inc.}
    \companybindercover{FANUC America Corporation}
    \companybindercover{Federal Aviation Administration}
    \companybindercover{FedEx SmartPost}
    \companybindercover{FEV, Inc.}
    \companybindercover{Fitbit}
    \companybindercover{Flagship Management LLC}
    \companybindercover{Fluxtrol, Inc.}
    \companybindercover{Ford Motor Company}
    \companybindercover{Freudenberg-NOK}
    \companybindercover{General Motors}
    \companybindercover{Gentex Corporation}
    \companybindercover{Gibbs \& Cox}
    \companybindercover{Google}
    \companybindercover{H.J. Heinz}
    \companybindercover{Harley-Davidson Motor Company}
    \companybindercover{Harman International}
    \companybindercover{Harris Corporation}
    \companybindercover{HDR Inc.}
    \companybindercover{HERE}
    \companybindercover{Huntington Ingalls Industries}
    \companybindercover{IAV Automotive Engineering, Inc.}
    \companybindercover{Inalfa Roof Systems Inc}
    \companybindercover{\url{Indeed.com}}
    \companybindercover{\url{Intrepidcs.com}}
    \companybindercover{IXL Learning}
    \companybindercover{Johns Hopkins University}
    \companybindercover{Johnson Controls}
    \companybindercover{JTEKT North America}
    \companybindercover{Keithley Instruments}
    \companybindercover{KLA-Tencor}
    \companybindercover{Lake Region Medical}
    \companybindercover{Laserfiche}
    \companybindercover{Lear Corporation}
    \companybindercover{Learning A-Z}
    \companybindercover{Lockheed Martin}
    \companybindercover{MAHLE Industries}
    \companybindercover{Manhattan Associates, Inc.}
    \companybindercover{Marine Officer Selection Team}
    \companybindercover{Masco Cabinetry}
    \companybindercover{Meridian Health Plan}
    \companybindercover{Michelin}
    \companybindercover{MIM Software}
    \companybindercover{MIT Lincoln Laboratory}
    \companybindercover{Mitsubishi Electric Automotive America}
    \companybindercover{Moeller Manufacturing Company, Incorporated}
    \companybindercover{Motorola Mobility}
    \companybindercover{Mu Sigma Inc}
    \companybindercover{NASA}
    \companybindercover{National Instruments}
    \companybindercover{National Security Agency}
    \companybindercover{Naval Research Laboratory}
    \companybindercover{NAVSEA}
    \companybindercover{Niowave, Inc.}
    \companybindercover{Norfolk Southern}
    \companybindercover{Novelis Inc.}
    \companybindercover{Olark}
    \companybindercover{Owens Corning}
    \companybindercover{P3 North America}
    \companybindercover{PACCAR Inc.}
    \companybindercover{PinnacleAIS}
    \companybindercover{Plastipak Packaging}
    \companybindercover{PolyOne Corporation}
    \companybindercover{PPG Industries}
    \companybindercover{Praxair, Inc.}
    \companybindercover{Procter and Gamble}
    \companybindercover{Procter and Gamble Manufacturing}
    \companybindercover{PwC}
    \companybindercover{PYRAMID SOLUTIONS, INC.}
    \companybindercover{Quantcast}
    \companybindercover{QuEST Global}
    \companybindercover{RelateIQ}
    \companybindercover{Rent The Runway}
    \companybindercover{RetailMeNot, Inc.}
    \companybindercover{Ricardo, Inc.}
    \companybindercover{Rithtech}
    \companybindercover{Rockwell Automation}
    \companybindercover{Rolls-Royce}
    \companybindercover{Ropes \& Gray}
    \companybindercover{SapientNitro}
    \companybindercover{SC Johnson}
    \companybindercover{Schaeffler Group USA}
    \companybindercover{Severstal North America}
    \companybindercover{Shell}
    \companybindercover{Shure, Inc.}
    \companybindercover{Silicon Laboratories, Inc.}
    \companybindercover{Skyworks Solutions, Inc.}
    \companybindercover{Soil and Materials Engineers, Inc.}
    \companybindercover{Spot Trading L.L.C.}
    \companybindercover{Square, Inc.}
    \companybindercover{State Farm}
    \companybindercover{TAC Manufacturing, Inc. (TRAM Group)}
    \companybindercover{TechSmith Corporation}
    \companybindercover{Tetra Tech}
    \companybindercover{The Boeing Company}
    \companybindercover{The Walsh Group}
    \companybindercover{Thomson Reuters}
    \companybindercover{TriggerMail}
    \companybindercover{TripAdvisor}
    \companybindercover{Trunk Club}
    \companybindercover{TRW Automotive}
    \companybindercover{U.S. Nuclear Regulatory Commission}
    \companybindercover{Union Pacific Railroad}
    \companybindercover{United Airlines}
    \companybindercover{Urban Science}
    \companybindercover{Variation Reduction Solutions, Inc.}
    \companybindercover{Vector CANtech}
    \companybindercover{Visa, Inc.}
    \companybindercover{VMware}
    \companybindercover{W.W. Grainger, Inc}
    \companybindercover{Walmart}
    \companybindercover{Walt Disney Parks \& Resorts}
    \companybindercover{West Monroe Partners}
    \companybindercover{Westinghouse Electric Company}
    \companybindercover{Williams International}
    \companybindercover{Wolverine Trading, LLC}
    \companybindercover{Brose North America, INC.}
    \end{document}